\chapter{Leap Motion controller}

\section{Controller}
Leap Motion is an USB sensor device, designed to provide realtime tracking of objects in three-dimensional space. It allows user to get information about objects located in devices' field of view (about 150 degree with distance not exceeding 1 meter).
%https://www.leapmotion.com/press_releases/leap-motion-to-launch-leap-motion-controller-exclusively-at-best-buy]. 

Details of how Leap Motion performs 3D scene capturing, have not been revealed by Leap Motion, Inc. Three infrared LEDs are used for scene illumination, while two cameras spaced 4 centimeters apart capture images with 50-200 fps framrate, dependant whether USB 2.0 or 3.0 is used.

-- photo -- 

\section{Data access}

Unlike Microsoft Kinect, Leap Motion does not provide access to raw data in form of a point cloud. Captured data is processed by propietary drivers supplied by vendor and accessible using an API. Leap Motion was intended to be a human-computer interface, not general purpose 3D scanner, so it is optimised for recognizing human hands or pointy objects.

The main data container we get from Leap Motion API is a Frame. Average framerate while using dual core laptop and USB 2.0 interface, is 50 frames per second. One frame consists of hands, fingers, pointables (objects directly visible by controller), and additional informations, like gestures recognized by simple built-in recognition mechanism, frame timestamp, rotation, translation and scaling data. 

For purposes of this project, we have created our own data format. It contains only information necessary for us and allows us to easily save captured frames to file, and read them later for processing and testing purposes.