\chapter*{Zasoby internetowe}\label{sect:web-resources}%
\phantomsection\addcontentsline{toc}{chapter}{Zasoby internetowe}

\newcommand{\tturl}{\begingroup \urlstyle{tt}\Url}

{\small
\begin{enumerate}[{[}A{]}]
	\item \label{hart} Project Gutenberg. \\
		\tturl{http://www.gutenberg.net}
	\item \label{aspectj} The AspectJ Project. \\
		\tturl{http://www.eclipse.org/aspectj/}
	\item \label{gauntlet}  The Gauntlet (Universal Robustness Corpus). \\
		\tturl{http://www.michael-maniscalco.com/testset/gauntlet/}
	\item \label{manzini-corpus} Manzini's Large Corpus. \\
		\tturl{http://www.mfn.unipmn.it/~manzini/lightweight/corpus/}
	% \item \label{carrot} Carrot2 Clustering Engine. \\
	% 	\tturl{http://carrot2.org/}
	% \item \label{jsa} Java Suffix Arrays. \\
	% 	\tturl{http://jsuffixarrays.org/}
	% \item \label{bsd} New BSD License \\
	% 	\tturl{http://www.opensource.org/licenses/bsd-license.php}
		
		
		\item \label{mori-benchmark} Yuta Mori, Suffix Array Construction Benchmark \\
			\tturl{http://homepage3.nifty.com/wpage/benchmark/index.html}

		\item \label{msufsort} Michael Maniscalco, The MSufSort Algorithm. \\
			\tturl{http://www.michael-maniscalco.com/msufsort.htm}

		\item \label{KScode} Peter Sanders, Skew algorithm. \\
			\tturl{http://www.mpi-inf.mpg.de/~sanders/programs/suffix/}


		\item \label{ssort}  M. Douglas McIlroy, ssort.c \\
			\tturl{http://cm.bell-labs.com/cm/who/doug/source.html}

			\item \label{archon} Dmitry A. Malyshev, Archon \\
				\tturl{http://kvgate.com/index.php?root/comp/arch/archon/}

			\item \label{MFcode} Giovanni Manzini, A Lightweight Suffix Array and BWT Construction Algorithm \\
				\tturl{http://web.unipmn.it/~manzini/lightweight/ds.tgz}
				
			\item \label{libdivsufsort} Yuta Mori, libdivsufsort project homepage. \\
				\tturl{http://code.google.com/p/libdivsufsort/}
				
				
			\item \label{LScode} N.Jesper Larsson, qsufsort.c \\
				\tturl{http://www.larsson.dogma.net/qsufsort.c}
				
\item \label{bpr-code}  Klaus-Bernd Sch\"{u}rmann i Jens Stoye, bpr downloadpage. \\
	\tturl{http://bibiserv.techfak.uni-bielefeld.de/download/tools/bpr.html}


		
\end{enumerate}
}
